Simulataneous Robot Localization and \\Environment Mapping with \\Simulated Sensor Measurements

### 2018-05-03 paper.tex
More Edits

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{F}{or} mobile robots, self-localization is extremely important. 
A robot must know its current state to properly perform its duties and maintain its operation. 
However, localization is non-trivial due to inherent inaccuracies in actuators and sensor 
systems, as well as non-ideal environments, which introduce other errors. Mapping unknown 
environments is equally important and poses similar problems as localization. Given that 
the robot location is known, it is difficult to build an accurate map of the environment 
because of noisy sensor measurements.

@@

In order to address this problem, Simulataneous Localization and Mapping (SLAM) techniques 
have been developed, which rely on probabilistic techniques to build probability 
distributions of expected positions of features and the robot in a map. SLAM algorithms 
have a vast number potential applications. For instance, they have been used to develop 
drone and land-based robotic systems capable of mapping disaster zones 
\cite{drone-response, mapping-disaster-areas}. Also, they are being used in autonomous cars to 
safely navigate traffic. Also, they have been used to build volumetric maps of complex mines
\cite{6d-mining-slam}.

There are three main paradigms for solving the SLAM problem: The Kalman Filter, the Particle 
Filter, and Graph-based solutions. The Kalman Filter is computationally the least intensive 
of these techniques, as it assumes that all sensor measurements and actuators have Gaussian 
noise distributions around their means. The Particle Filter utilizes Monte Carlo techniques 
to estimate the state of the robot. Graph-based solutions assume the objects around the robot 
can be approximated to a course grid landscape. \cite{prob-robots}

@@

The simulation for the Extended Kalman Filter is demonstrated through an abstract robot which 
can sense the two-dimensional environment through multiple different types of sensors. To 
simulate the NASA RMC robot, the robot can sense the state of itself and the environment 
obstacles through multiple abstracted types of sensors, including:

\begin{itemize}
 \item An X-Box Kinect, which can detect the location of all obstacles.
 \item A gyroscope, which can determine the robot’s orientation relative to its previous frame.
 \item An Aruco Marker, which can determine the robot’s location relative to the origin (which is 
       where the marker is located).
 \item Encoders, which can determine the robot’s location relative to the previous frame. 
\end{itemize}

The Robot class (in Robot.h) represents the actual position of the robot inside its environment. 
From here, the robot can make ``measurements'' with respect to its various sensors. These 
measurements, which can be called from methods such as \texttt{getGyroMeasurement()} and 
\texttt{getArucoMeasurement()}, simply return the respective quantities the sensor is trying to 
measure, plus some zero-mean noise with a preset standard deviation. For instance, when the 
robot calls to its function \texttt{getArucoMeasurement()} while located at \texttt{(1, 1)}, the 
function may return the vector \texttt{(1.03, 0.99)} as a result of the applied sensor noise.

@@

\texttt{EKFSlammer} stores the robot's and environment's state $x_t$ in a \texttt{VectorXd}. The
perceived position and orientation of the robot, as well as the location of the obstacles in the map, 
can be expressed informally as 
\begin{equation*}
 x_t = \left[\begin{IEEEeqnarraybox*}[][c]{,c,}
        \vec{s} \\
        \theta \\
        \vec{i}_1 \\
        \vec{i}_2 \\
        \vdots
        \end{IEEEeqnarraybox*}\right],
\end{equation*}
where $\vec{s}$ is the robot's location with respect to the Aruco Marker (the arbitrarily-defined
origin) and $\vec{i}_n$ is the location of the $i$\textsuperscript{th} obstacle. The vectors represented
in code for measurement updates are the Kinect measurement vector and the gyroscope measurement vector.
The Kinect senses all obstacles in the environment; therefore, its measurement vector for all $i$ obstacles 
is expressed as
\begin{equation*}
 z_{t,K} = \left[\begin{IEEEeqnarraybox*}[][c]{,c,}
           r_1 \\
           \theta_1 \\
           r_2 \\
           \theta_2 \\
           \vdots \\
           r_i \\
           \theta_i
           \end{IEEEeqnarraybox*}\right] + \vec{\epsilon_t},
\end{equation*}
and the gyroscope measurement vector can be expressed as 
\begin{equation*}
 z_{t,g} = \omega_t + \epsilon_t,
\end{equation*}
where $\omega_t$ is the angular velocity of the robot, and $\vec{\epsilon_t}$ and $\epsilon_t$ are the 
normally-distributed noise factors for each sensor.

First, to generate the \textit{a priori} estimate, the \texttt{motionModelUpdate()} method is called by 
\texttt{ekfUpdate}. Its parameters are the timestep for the robot and its control parameters, in 
the form of a forward velocity and an angular velocity (i.e. the \texttt{controlIn} struct; see 
\texttt{Utils.h}). The \texttt{motionModelUpdate} will recalculate the estimated state of the 
robot, given the control input and given the known uncertainties of the robot's actuators 
(i.e. the robot's wheels, since this robot can only move).

@@

>>>>

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by the IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{F}{or} mobile robots, self-localization is extremely important. 
A robot must know its current state to properly perform its duties and maintain its operation. 
However, localization is non-trivial due to inherent inaccuracies in actuators and sensor 
systems, as well as non-ideal environments, which introduce additional errors. Robotic mapping of unknown 
environments is equally important and poses similar problems as localization. Given that 
the robot location is known, it is difficult to build an accurate map of the environment 
due to noisy sensor measurements.

@@

In order to address this problem, Simulataneous Localization and Mapping (SLAM) techniques 
have been developed, which rely on probabilistic methods to build probability 
distributions of expected positions of features and the robot in a map. SLAM algorithms 
have a vast number of potential applications. For instance, they have been used to develop 
drone and land-based robotic systems capable of mapping disaster zones 
\cite{drone-response, mapping-disaster-areas}. They are being used in autonomous cars to 
safely navigate traffic. Also, they have been used to build volumetric maps of complex mines
\cite{6d-mining-slam}.

There are three main paradigms for solving the SLAM problem: The Kalman Filter, the Particle 
Filter, and Graph-based solutions. The Kalman Filter is computationally the least intensive 
of these techniques, as it parameterizes the distributions, assuming that the robot pose and landmark positions follow a Gaussian distribution. The Particle Filter utilizes Monte Carlo techniques 
to estimate the state of the robot. Graph-based solutions assume the objects around the robot 
can be approximated to a course grid landscape. \cite{prob-robots}

@@

The simulation for the EKF SLAM algorithm is demonstrated through an abstract robot which 
can sense the two-dimensional environment through multiple types of sensors. To 
simulate the NASA RMC robot, the robot can sense the state of itself and the environment 
obstacles through multiple abstracted types of sensors, including:

\begin{itemize}
 \item A Microsoft Kinect, which returns a range-bearing measurment to all obstacles.
 \item A gyroscope, which can determine the robot’s angular orientation relative to its previous frame.
 \item A camera capable of determining the position of a fiducial marker placed on the collector bin.
 \item Encoders, which can determine the robot’s location relative to the previous frame. 
\end{itemize}

The Robot class (in Robot.h) represents the actual position of the robot inside its environment. 
From here, the robot can make ``measurements'' with respect to its various sensors. These 
measurements, which can be called from methods such as \texttt{getGyroMeasurement()} and 
\texttt{getArucoMeasurement()}, simply return the respective quantities the sensor is trying to 
measure, plus zero-mean gaussian noise with a preset standard deviation.  For instance, when the 
robot calls to its function \texttt{getArucoMeasurement()} while located at \texttt{(1, 1)}, the 
function may return the vector \texttt{(1.03, 0.99)} as a result of the applied sensor noise. The standard deviations were determined by collecting measurement samples from the various sensors and generating the sampling distribution.

@@

\texttt{EKFSlammer} stores the robot's and environment's state $x_t$ in a \texttt{VectorXd}. The
perceived position and orientation of the robot, as well as the location of the landmarks in the map, 
can be expressed as 
\begin{equation*}
 x_t = \left[\begin{IEEEeqnarraybox*}[][c]{,c,}
        \vec{s} \\
        \theta \\
        \vec{m}_1x \\
        \vec{m}_1y \\
        \vdots
        \end{IEEEeqnarraybox*}\right],
\end{equation*}
where $\vec{s}$ is the robot's location with respect to the Aruco Marker (the arbitrarily-defined
origin) and $\vec{m}_i$ is the location of the $i$\textsuperscript{th} landmark.

First, to generate the \textit{a priori} estimate, the \texttt{motionModelUpdate()} method is called by 
\texttt{ekfUpdate}. Its parameters are the timestep for the robot and its control parameters, in 
the form of a forward velocity and an angular velocity (i.e. the \texttt{controlIn} struct; see 
\texttt{Utils.h}). The \texttt{motionModelUpdate} calculates the estimated state of the 
robot, given the control input and the known uncertainties of the robot's actuators.

@@

 The vectors represented
in code for measurement updates are the Kinect measurement vector and the gyroscope measurement vector.
The Kinect senses all obstacles in the environment; therefore, its measurement vector for all $i$ obstacles 
is expressed as
\begin{equation*}
 z_{t,K} = \left[\begin{IEEEeqnarraybox*}[][c]{,c,}
           r_1 \\
           \theta_1 \\
           r_2 \\
           \theta_2 \\
           \vdots \\
           r_i \\
           \theta_i
           \end{IEEEeqnarraybox*}\right] + \vec{\epsilon_t},
\end{equation*}
and the gyroscope measurement vector can be expressed as 
\begin{equation*}
 z_{t,g} = \omega_t + \epsilon_t,
\end{equation*}
where $\omega_t$ is the angular velocity of the robot, and $\vec{\epsilon_t}$ and $\epsilon_t$ are the 
normally-distributed noise factors for each sensor.
